\section{Sprint 4}

\subsection{Time Frame}
When we didn't finish implementation by the end of Sprint 3, we had to add another sprint.

The time frame for Sprint 4 was week 44 and 45. We started the sprint on October 28th with a weekly supervisor meeting. On November 6th we had a Skype meeting with the customer. We finished the sprint on November 8th. After the sprint, on November 13th, we held an acceptance meeting with the customer.

\subsection{Original Plan}
Because we had planned to finish within three sprints, there were originally no plans for Sprint 4. However we quickly realized that we were going to need a Sprint 4 due to having an incomplete product at the end of Sprint 3.

\subsection{Revised Plan}
The fact that we knew this would be the last sprint we had time for let us skip the sprint planning meeting because we knew that everything that was to be implemented that had not yet been, had to be done during this sprint.

\subsection{Development}
In this sprint, we converted the existing MVC controller of our implementation to a Web API controller, and generated documentation with Doxygen.

\subsection{Other Work}
We made the final outline of the report, and discussed which sections (including chapters and subsections) that we needed to include or rework before the final delivery.

The technical documentation needed to be completed along with the product, so we had to go through each method and write XML Documentation Comments on each of them.

The architectural documentation that was created in the beginning did not reflect the changes we had made to the product due to architectural erosion, and needed to be updated to better the reflect the actual system implemented.

\subsection{Backlog}
In the sprint, we finished the implementation and had the acceptance meeting with the customer. Therefore, the most important thing to focus on after Sprint 4 is the report.

\subsection{Customer Meeting}
We had a customer meeting with the Asle on November 6th where we showed him the MVC controller we made, how it interacted with the database and how data was sent from one view to another. Due to the fact that Asle was still in Spain we had to do the customer meeting through Skype (video conferencing software).

\subsection{Retrospective}
We weren't happy that we had to do a Sprint 4, because we had hoped that we would be finished with the implementation after Sprint 3. The conversion of the MVC controller to the API controller yielded problems we didn't expect, and it should have gone more smoothly. Unfortunately we had to rewrite a lot of the code due to big differences between the controllers.