\section{Preliminary Studies}
This section contains the information we found in our preliminary studies, and the choices we made from the information we gathered. Covered here are process-related topics such as development methodology, pros and cons of these, and which we chose, as well as technology-related topics such as frameworks and standards.
\subsection{Development Methodology}
The customer driven project proposes two types of development methodologies, the sequential waterfall method, and the agile scrum.
\subsubsection{Waterfall}
The waterfall development method is a sequential design process. It is divided into clearly defined, mostly separated phases, although there is often some overlap between them. The first phases focus on gathering requirements and writing initial documentation like design/architecture. Later phases move on to actual implementation, then testing, followed by final report. Maintenance after a "completed" project might also in some cases be part of the process. <add figure depicting process>
\subsubsection{Scrum}
The scrum development method is an agile approach to development. It is an iterative process, consisting of several cycles of most of the phases of a sequential method, each cycle resulting in a functioning prototype. <add figure depicting process>
\subsubsection{What we have chosen}
%\begin{tabular}{| l | l |}
   % \hline
    %\textbf{Waterfall} & \textbf{Scrum}\\ \hline
   % Bad stuff & Good stuff \\ \hline
  %\end{tabular}
Different sides of each of the proposed methods make the respective methods a better or worse fit for our project than the other method. We have highlighted the most important of these points below, leading to a conclusion and our choice of method.
\begin{itemize}
	\item Waterfall
	\begin{itemize}
		\item Is a good method if you know everything about the project beforehand, or are able to acquire the required information and the full project specification before the implementation phase. Due to the course schedule and the relatively limited time frame of our project, we felt we needed to start implementation earlier than a long planning and requirements phase would allow.
		\item Is suitable for small projects, since they are manageable to plan fully. This fits our project description.
		\item Little underway feedback, which could fit if access to customer was restricted, but specifications are expected to remain the same. While the specifications for the project are expected to remain unchanged, our goal was to include the customer in the process.
		\item Supplies strong documentation as the first phases are focused entirely on creating these documents. However, while the course relies heavily on documentation, the customer had no use for most of this documentation.
		\item Structured workflow. What you see is what you get.
		\item It's easier to get every involved party on the same page with a thorough plan. This is beneficial to any project, but even more so in a project like ours, where the team consists of students who may have other projects in other courses running in parallel with this.
	\end{itemize}
\end{itemize}
\begin{itemize}
	\item Scrum
	\begin{itemize}
		\item Supports rapid production of prototypes to show the customer. This allows for easier correction of misunderstandings, because they become apparent earlier through the functioning prototypes.
		\item Heavily reliant on easy access to the customer for continous feedback and extraction of requirements. This is okay for our project, as our customer is readily available through both e-mail and phone. % We should probably do something about the tense of sentences. Always past or always present?
		\item This approach was suggested by the customer, and is the same as they use. Using the same method as the customer might be beneficial to the project, as it improves communication and workflow.
		\item The method utilizes stand-up meetings, a scrum master, and optionally (and preferably) a kanban/scrum board. These things do carry overhead, but provide both the team and customer with frequent feedback, making it both a pro and a con.
		\item Handles change to requirements very well. Might cause us to plan for unnecessary change, but quite a few necessary changes are expected underway; which makes this a fit for our project. %TODO
		\item Can use online tools where both parties can review/interact with the planning and prioritization %TODO
		\item Relies on experience with the full development process if it’s to cover the entirety of the project %TODO
	\end{itemize}
\end{itemize}
In conclusion, we ended up with a mix of the two methods. %TODO
\subsection{Frameworks}
\subsubsection{Software Development Model}
\subsubsection{Programming languages, Communication Protocols and File Formats}
\subsubsection{Web Api}
\subsubsection{Server}
\subsubsection{Database}
We had a lot of problems with the database, the customer said he'd put up a database server for us to use. However this turned out to be difficult to achieve due to the security/confidentiality issues on their server. We had to try to set up the database server ourself on our local machine, this proved to be rather difficult due to microsoft tools not giving enough information, and thereby not installing the necessary tools.     
The customer uses a MSSQL server and they provided an 11GiB .bak file which we could use to restore the database.
\subsection{Extra Tools}
\subsection{Existing Technology}
\include{chapters/preliminary_studies/technology}
\subsection{Standards}
\include{chapters/preliminary_studies/Templates_and_Standards}
\subsection{Summary}