\chapter{Evaluation}
In this chapter we will evaluate the whole project and our process during the project to see how what we felt was done correctly and what could have been done better. This chapter will also take a look at our group dynamic and analyze how we handled issues and risks.

\newpage
\section{The Process}


\section{Quality Assurance}
\subsection{External Communication}
This sub chapter is mainly about communication with people outside of our group.
\subsubsection{Communication with the Customer}
The customer was always available via e-mail and whenever we needed him urgently we could call him via mobile phone, which was available via the assignment text in the compendium.

The customer answered rapidly (usually with minutes), but there was one occurrence during his vacation when we didn't receive a response to our e-mails for a couple of days. We thought that he didn't have an internet connection available, however it soon turned out to be our mail having ended up in his spam folder.

Asle, the customer's main representative, is a computer scientist himself, which was beneficial for us because he could give precise answers to our questions, rather than the more vague answers one often gets from less technologically inclined customers. He was also a student at NTNU a few years back, which turned out to be quite beneficial for us because he was familiar with the university and its processes. This saved us time and trouble e.g. when letting him know where meetings would take place.

In the customer meeting in Sprint 1 we got an demonstration of the database structure. The other customer representative, Hans Ormberg, suggested that picture upload to the database was also a good idea to implement which Asle agreed with. We on the other hand kept this in the backlog and would implement it if we had the time to do so. When it turned out that we didn't, we let Asle know that we had to drop the picture upload implementation due to time constraints. He understood the situation, and let us know it was not a problem, because this was not a requirement in the original assignment.

\subsubsection{Supervisor}
Our supervisor, Meng Zhu, was in the beginning not very responsive via mail. It would typically take a couple of days before we received a response from him. We mentioned it to him in a supervisor meeting that we wanted a mail response within 24 hours of him receiving the mail. He let us know he would fix this issue, and after that, all the mails that needed a response was responded to in less than 24 hours after we sent the mail. Most of our communication with Meng was through the supervisor meetings where he went through our weekly report and minutes from the previous meeting. He also asked us if there were any unresolved issues we need help with to fix. 

Meng was also concerned with how our report would turn out, and asked us if we could make a draft layout of the final report so he could double check that we had included all the chapters and sections we needed for a well written and complete report. If we needed resources to fulfill a chapter in our report Meng gladly offered to lend us one of his system development books. 

When we had the first meeting with our supervisor we received a template that we should use for the weekly reports. This template saved us time whenever we created a weekly report for the supervisor meeting, and it made it easier for to be more efficient on the meeting so we could focus on the assignment, although we sometimes forgot to remove parts from the template that weren't applicable for that particular weekly report.

\subsection{Internal communication}
We had no set rules in our group, and instead followed common group sense, e.g. notifying the other group members if we were late. We didn't have issues with people being 2 hours late, because we knew that they might have other subjects that might need to be prioritized at that time. Deliveries in other subjects might lead to sleepless nights, making meeting the group for working on the project at 8:00 in the morning not feasible. We did however call or contact the person if he didn't appear after a while when we had agreed to meet, in case he had simply overslept, or to make sure he would be in time for a meeting with the customer or our supervisor. We didn't punish any late arrivals due to all of us being late in turn, and experience no problems with this.
There were no issues in our internal group, and usually agreed on everything.


\section{Implementation}
Our implementation followed the clean code principle and template written on \ref{Templates and Standards section} Templates and Standards on page \pageref{Templates and Standards section}. This ensured that the code followed the standard and was readable for other developers. All the methods we implemented had XML Style Comments for documentation purposes.

We would hope the implementation of our code had went more smoothly than "error message per third line of written code", but when we finally got somewhat of a grasp of C\# and Web API, things started to go a little more smoothly.

Due to our version control system with Git and GitHub we could easily experiment with the code without ruining the project, because Git let us revert the changes made. Even if we wrote on the same file we had no large Git conflicts that needed a lot of rework to fix the merge. It was usually just removing the "< < < < <HEAD" section that Git added.

\subsection{Testing}
We had no specific test plan. The implementation of our code needed a pdf accompanied by a lot of data. These data had to be checked against the database and we had to make sure that all the data was in the correct format both to the database and the input data. We had to make sure to give an appropriate error message otherwise. The testing was done while developing, and we usually got a lot of error messages, but when the code ran we could easily check if the result was as expected or not by sending data to the IIS Express server via a web form we created locally for testing.

\section{Group dynamics}
Our group had issues with people being late, but because we all were late now and then it was not a problem that irritated any of us. The group was also fortunate that all the group members are from the same class (Computer Science fourth year), so everyone knew each other before we started working. The whole group had also been together on a class trip to Japan before this project, where we got to know each other better outside of school. This helped immensely on the group dynamic. We therefore felt that the group dynamic course didn't give us as much as we had hoped for. The group dynamic course did however give us insight of our group and helped us defining roles and responsibility amongst us.



\section{Risk management}
All group projects have risks, this is inevitable. Check \ref{internalRisks} Internal Risks on page \pageref{internalRisks} and \ref{externalRisks} External Risks on page \pageref{externalRisks}. The most important risks are mentioned below.

\begin{itemize}
\item The highest risk was our unfamiliarity with the technology \\ We faced this problem by using Googling the problem at hand if possible and if this didn't work out we asked our customer Asle if he knew how to fix the problem.
\item Development and Implementation \\ Development didn't go as we had hoped. There were a lot of bugs and hiccups when we implemented the code due to familiarity of the system. However tons of debugging helped us get a better grasp of the whole project and system.
\item Other subjects \\Due to all of us being a forth grader, we have a lot of other subjects which tends to have big deliveries and/or projects which counts toward the final score in that course. Therefore other subjects had to be prioritized now and then. We mostly had to accept this and try to compensate for the lost time.
\item Illness \\ There's not much one can do with illness, the risk of being ill is especially high in the fall semester due to the weather change from summer to winter. The best thing to do as an ill person is to stay at home and fully recover as fast as possible. 
\end{itemize}
These risks that were the most risky ones was not a big factor for the end product. We had a buffer in Sprint 3 and Sprint 4 was added as another buffer in case we needed it.
